Effect_size_families

### 2020-06-26 Thesis_Chapter_1/Supp_Material.Rmd
Supplementary mat

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, out.width = "100%", fig.align='center'}
setwd("~/R_projects/Hp_pollen_experiment")

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
library(ggplot2)
setwd("~/R_projects/Hp_pollen_experiment")
total_pollen <- read.csv("Data/Csv/total_pollen.csv")
ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
  geom_bar(stat='identity', position='dodge')+theme_minimal()+
  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
par(mar=c(30,13,2,4),xpd=F)
setwd("~/R_projects/Hp_pollen_experiment")
data_percentage <-readRDS("Data/RData/per.RData")
data_percentage=as.matrix(data_percentage)
coul = c("#999999","#779799")
barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
 "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
abline(v=50,col="black")

#lines(c(0,10),50,col="red")
```

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
par(mar=c(2,13,2,4),xpd=F)
par(mfrow=c(3,1))
setwd("~/R_projects/Hp_pollen_experiment")
ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E. sativa-I. purpurea", "B. oleracea-I. purpurea","B. rapa-I. purpurea", "S. alba-I. aquatica", "S. alba-S. melongena", "E. sativa-P. integrifolia", "B. rapa-S. lycopersicum", "B. oleracea-C. annuum"))
abline(v=50,col="black")
legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(8.3,6.8,"A) Brassicaceae")
ratio_con <-readRDS("Data/RData/ratio_con.RData")
barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I. purpurea-S. melongena","I. aquatica-C. annuum","I. purpurea-E. sativa","I. aquatica-S. alba"))
abline(v=50,col="black")
legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(9,3.5,"B) Convolvulaceae")

ratio_sol <-readRDS("Data/RData/ratio_sol.RData")
barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C. annuum-I. purpurea", "S. melongena-I. aquatica", "P. integrifolia-I. aquatica", "S. lycopersicum-I aquatica","S. melongena-E. sativa", "P. integrifolia-E. sativa", "C. annuum-S. alba", "S. lycopersicum-B. rapa"))
abline(v=50,col="black")
legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(6.8,6.8,"C) Solanaceae")

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, fig.align='center', fig.cap="Fig S5"}

#Here I try to compare the different proportions of pollen between the different groups
#I use Tukey method

library(lme4)
library(emmeans)
library(reshape2)
library(multcompView)
library(lsmeans)
library(multcomp)
library(ggplot2)
library(DHARMa)
setwd("~/R_projects/Hp_pollen_experiment")

total_pollen <- read.csv("Data/Csv/total_pollen.csv")

total_pollen=total_pollen[,-1]
colnames(total_pollen)[3] <- "pollen"
#head(total_pollen)

# Dividing by focal pollen and non focal pollen
# In order to compare pollen as donor and recipient per family 
pollen_foc <- subset(total_pollen, variable=="focal_pollen")
pollen_non <- subset(total_pollen, variable=="non_focal_pollen")

total  <- as.numeric(pollen_foc$pollen) + as.numeric(pollen_non$pollen)
pollen_non$total_pollen  <- total
pollen_non$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
pollen_non$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")

pollen_non <- pollen_non[,-c(1,2)]
colnames(pollen_non)[1] <-"hp_pollen"
pollen_non$hp_ratio <- as.numeric(pollen_non$hp_pollen)/as.numeric(pollen_non$total_pollen)
#hist(pollen_non$hp_ratio)

pollen_foc$total_pollen  <- total
pollen_foc$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
pollen_foc$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")

pollen_foc <- pollen_foc[,-c(1,2)]
colnames(pollen_foc)[1] <-"hp_pollen"
pollen_foc$hp_ratio <- as.numeric(pollen_foc$hp_pollen)/as.numeric(pollen_foc$total_pollen)
#hist(pollen_foc$hp_ratio)

#Analyse data and plot it

junk.glmer = lm(hp_ratio ~ fam_non, data = pollen_non)
#plot(junk.glmer)
#goodness of fit of the model
#testDispersion(junk.glmer)
#simulationOutput <- simulateResiduals(fittedModel = junk.glmer, plot = T)

#lsm = lsmeans(junk.glmer, "fam_non", type = "response")
#pairs(lsm)
#CLD <- CLD(lsm,alpha=0.05,adjust="tukey")

#ggplot(CLD,aes(x= fam_non,y= lsmean,
#label = .group)) +theme_minimal()+
#geom_point(shape  = 15,size   = 4) +ggtitle("B) Comparison of ratios as donor")+
#geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
#width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+
#geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black")

#Analyse data and plot it
junk.glmer = lm(hp_ratio ~ fam_foc, data = pollen_foc)
lsm = lsmeans(junk.glmer, "fam_foc", type = "response")
#pairs(lsm)
CLD <- CLD(lsm,alpha=0.05,adjust="tukey")

#theme
theme_ms <- function(base_size=12, base_family="Helvetica") {
  library(grid)
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.3)),
            axis.text=element_text(size = rel(1), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.8, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_line(),
            panel.grid.minor.y= element_blank()
      ))
}

par(mfrow=c(2,2))
ggplot(CLD,aes(x= fam_foc,y= lsmean,
               label = .group)) +theme_ms()+
  geom_point(shape  = 15,size   = 4) +ggtitle("")+
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
                width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+ geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(axis.text.x = element_text(size=14, face="bold"))

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, out.width = "100%", fig.align='center', fig.cap="Fig S6"}
setwd("~/R_projects/Hp_pollen_experiment")

### 2020-06-26 Thesis_Chapter_1/Supp_Material.tex
Supplementary mat

\captionsetup[figure]{labelformat=empty}

\captionsetup[table]{labelformat=empty}
\renewcommand{\figurename}{}

@@

\begin{center}\includegraphics[width=1\linewidth]{Supp_Material_files/figure-latex/unnamed-chunk-4-1} \end{center}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{S7}
\end{figure}

>>>>

\captionsetup[figure]{labelformat=empty}
\captionsetup[table]{labelformat=empty}
\renewcommand{\figurename}{}

@@

\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}

\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}

\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}

\begin{figure}

{\centering \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-7-1}

}

\caption{Fig S5}\label{fig:unnamed-chunk-7}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{Supp_Material_files/figure-latex/unnamed-chunk-8-1}

}

\caption{Fig S6}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{S7}
\end{figure}
